### 2015-05-05 background.tex
more updates in the background section

Figure~\ref{fig:locksets} shows an example of applying lockset analysis on a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing the same shared variable $A$. Thus, we have to track three locksets: the current locksets $\mathit{CLS}_1$ and $\mathit{CLS}_2$ for $T_1$ and $T_2$ respectively; and the lockset $\mathit{LS}_A$ for $A$. Initially, $\mathit{LS}_A$ contains the two locks $M$ and $N$ that the two threads acquire during execution. When $T_1$ terminates, $\mathit{LS}_A$ contains only the lock $N$, because the thread write accessed $A$ without holding $N$. Next, during the execution of $T_2$, the thread write accesses $A$ without holding $M$. Thus, $\mathit{LS}_A$ becomes the empty set. This means that there is a potential data race between the two threads on $A$ as $T_2$ does not consistently protect $A$ with at least one common with $T_1$ lock.

>>>>

Figure~\ref{fig:locksets} shows an example of applying lockset analysis on a concurrent program consisting of two threads $T_1$ and $T_2$, both accessing a global variable $A$. Initially, $\mathit{LS}_A$, which is the lockset for A, contains all possible locks in the program: $M$ and $N$. During execution of $T_1$, the thread writes $A$ without holding $N$, and thus $N$ is removed from $\mathit{LS}_A$. Next, during execution of $T_2$, the thread writes $A$ without holding $M$, and thus $\mathit{LS}_A$ becomes empty. Finally, a warning is reported because the two threads do not consistently protect $A$.
